% !TEX root = ../Report.tex
% ======================================================================
\chapter{Introduction}
% ======================================================================

This report presents the design, implementation, testing, and evaluation of
\textit{GiTrip}, a web application for collaborative trip planning with
Git-like version control semantics. The core premise is that itineraries change
in ways similar to software artefacts: multiple contributors propose
alternatives, edits happen in parallel, and the history of decisions matters.
In conventional trip-planning workflows, these properties are handled informally
through screenshots, chat messages, and manual copy-pasting across documents,
which makes the process fragile and difficult to audit.

\section{Problem Context and Motivation}
Trip planning is inherently multi-constraint: a feasible itinerary must account
for travel time between destinations, opening hours, stay durations, and daily
activity limits. For group trips, coordination adds an additional dimension:
multiple people make edits simultaneously, propose alternatives, or revise plans
after new information emerges. The absence of a robust change-management model
leads to common failure modes, such as overwritten edits, confusion about what
changed and why, and difficulty exploring alternatives without destabilising the
``main'' plan.

Mapping and routing tools such as Google Maps support route optimisation but
largely focus on a single itinerary at a time and do not provide structured
collaborative versioning for itinerary artefacts \cite{ref_google_maps}. Generic
collaboration tools such as Google Docs can support co-authoring, but they
provide limited structure for route and schedule constraints, and they do not
provide domain-specific merge semantics for itineraries \cite{ref_google_docs}.
GiTrip addresses this gap by combining: (i) itinerary-aware scheduling and
routing; (ii) Git-inspired branching and merging; and (iii) an interaction model
that remains accessible to users who do not know Git.

\section{Project Overview}
GiTrip is a server-rendered web application (Node.js + Express) that models a
trip as a repository and stores each saved version as a commit containing a full
snapshot of the trip plan. Users can create branches to explore alternate
itineraries, compare versions, and merge changes with a three-way merge. When
conflicts occur, GiTrip provides a dedicated merge user interface that allows
users to choose resolutions rather than silently overwriting information.

The system additionally includes:
\begin{itemize}
  \item An automatic scheduler that generates a feasible multi-day itinerary
        using routing durations and user constraints.
  \item Interactive plan editing via a timeline editor (arrival/departure times)
        and a map editor (coordinates).
  \item ``Easy mode'' UX that hides Git-specific vocabulary and advanced controls
        for non-technical users.
  \item A public gallery and star mechanism for browsing and lightweight social
        interaction.
  \item Export features (PDF via browser print, iCalendar export).
  \item Progressive Web App (PWA) capabilities and offline support.
\end{itemize}

\section{Objectives and Significance}
The project objectives were initially formalised using a MoSCoW prioritisation
in the Project Specification (Must/Should/Could/Won't). The Must-have objectives
included repository history, an optimised automatic scheduler, routing
integration, interactive visualisation, and merging with conflict resolution.
These objectives were chosen because they jointly define GiTrip's distinctive
contribution: no single competitor product simultaneously provides (a) itinerary
scheduling with constraints, (b) collaborative change history, and (c) Git-style
branching and merging semantics in the trip-planning domain
\cite{ref_wanderlog,ref_furkot,ref_roadtrippers,ref_tripit,ref_google_travel}.

A key boundary condition is that the original scope intentionally excluded
AI-powered itinerary generation from natural language. This decision was stated
as a Won't-have requirement to prioritise deterministic, inspectable scheduling
behaviour, and to avoid expanding scope into content recommendation and personal
preference modelling. The second assessor's Progress Report feedback suggested
investigating machine learning to strengthen the project; this report therefore
discusses AI as future work while justifying why it was not appropriate for the
Minimum Viable Product (MVP) scope.

\section{Contributions}
The technical contributions of this project are:
\begin{itemize}
  \item A repository and snapshot-based storage model for itinerary versions,
        enabling fast branch switching and reproducible restores.
  \item A three-way merge engine for itinerary snapshots, including conflict
        detection for time clashes, deletions, and selected non-time fields, plus
        a corresponding conflict-resolution UI.
  \item A constraint-aware auto-scheduler that integrates travel-time estimation,
        opening-hours nudging, desired windows, and spillover across days.
  \item A dual-path user interface (Easy mode vs Git mode) supporting both novice
        and power-user workflows.
  \item A deployed web system with practical security measures (sessions, CSP,
        rate limiting) and supporting features (weather, travel alerts,
        checklists).
\end{itemize}

\section{Report Structure}
Chapter 2 reviews related tools and foundational concepts. Chapter 3 describes
requirements and the rationale for the MoSCoW objectives. Chapter 4 outlines the
development methodology and evaluation strategy. Chapters 5 and 6 present the
system design and implementation. Chapter 7 summarises the testing strategy and
evidence. Chapter 8 reports Evaluation Day results and survey findings. Chapter 9
concludes with limitations and future work, followed by appendices containing
supporting evidence.
