% !TEX root = ../Report.tex
% ======================================================================
\chapter{Methodology}
% ======================================================================

This chapter explains the development process, tool selection, testing
methodology, and evaluation design used to deliver GiTrip.

\section{Development Approach}
GiTrip was developed using an iterative process combining:
\begin{itemize}
  \item \textbf{Risk-driven prototyping:} early prototypes validated feasibility
        of snapshot storage, server-rendered UI, and routing integration.
  \item \textbf{Incremental feature delivery aligned to MoSCoW:} Must-haves were
        implemented first to reach an end-to-end MVP; Should-haves and hardening
        tasks followed.
  \item \textbf{Continuous feedback:} weekly supervisor meetings provided
        checkpoints for scope, presentation, and evaluation readiness.
\end{itemize}

This approach was chosen because the project's key risks were
integration-heavy: routing APIs, interactive UI behaviour, and merge correctness
under edge cases. In particular, the merge engine required three major rewrites
as edge cases emerged during testing, which validated the decision to iterate
early on high-risk components.

\section{Choice of Tools and Technologies}
GiTrip's major technology choices were guided by the requirement to deliver a
complete, deployable web system with both server-rendered UI and asynchronous
planning/merge operations.

\subsection{Node.js and Express}
Node.js provides a mature ecosystem for web servers, with excellent support for
JSON-based data models \cite{ref_node_about}. Express was selected as a
lightweight, widely-used framework that supports both HTML routes and JSON APIs
cleanly \cite{ref_express}. This combination enables server-rendered views (for
fast initial load and SEO-like discoverability) while still allowing interactive
enhancements via client-side JavaScript.

\subsection{SQLite for Persistent Storage}
SQLite was chosen for persistent storage because it is reliable, lightweight, and
appropriate for a project deployed as a single web service
\cite{ref_sqlite_about}. Its file-based deployment model aligns with container
deployment and makes backups simple. While SQLite is not a distributed database,
GiTrip's collaboration model (branch-and-merge) does not require multi-writer
database replication; concurrency is managed at the application level.

\subsection{Mapping and Geocoding}
Leaflet was used for the interactive map because it is a well-established
open-source mapping library that integrates cleanly with OpenStreetMap tiles
\cite{ref_leaflet,ref_osm}. Nominatim was used for place lookup and geocoding
due to its OpenStreetMap integration and accessible API \cite{ref_nominatim}. A
server-side proxy route is used to apply rate limiting and caching to avoid
overloading the upstream service.

\subsection{Routing Providers}
OpenRouteService was used for travel-time matrix routing for non-transit modes,
which is important for ordering and scheduling decisions \cite{ref_ors_matrix}.
Google Directions API was used for public transit legs, because transit routing
requires schedule-aware directions and detailed steps for UI explanation
\cite{ref_google_directions_api}. A key design requirement was provider fallback:
when API calls fail, GiTrip can degrade gracefully using Haversine-based
estimates and constant-gap defaults.

\subsection{Usability Frameworks}
Nielsen's usability principles were used as a practical heuristic framework for
iterative UI refinement \cite{ref_nielsen}. WCAG 2.2 was used to guide
accessibility checks and avoid critical issues \cite{ref_wcag22}. For evaluation
design, SUS and TAM-inspired constructs were used to capture perceived usability
and acceptance \cite{ref_tam_davis}.

\section{Testing Strategy}
Testing was treated as a first-class requirement due to the complexity of merge
logic and scheduling constraints. The strategy combined:
\begin{itemize}
  \item \textbf{Unit tests} for opening-hours parsing, time utilities, and merge
        conflict detection.
  \item \textbf{Functional tests} covering end-to-end workflows (plan, commit,
        branch, merge, resolve, export).
  \item \textbf{Non-functional checks} covering security headers, rate limiting,
        and accessibility considerations.
\end{itemize}

All unit tests use the Node.js native test framework (\texttt{node:test}) with
strict assertions.

\section{Evaluation Design}
Evaluation was conducted via:
\begin{itemize}
  \item \textbf{User Acceptance Testing (UAT)} on Evaluation Day with an observer
        checklist recording objective task completion, time-to-finish, and hints
        given.
  \item \textbf{A post-demo survey} (Microsoft Forms) collecting Likert responses
        (including SUS), Git familiarity, and free-text feedback.
\end{itemize}

This design intentionally combines objective evidence (task completion and time)
with subjective user perception (usability and perceived value), aligning with a
pragmatic interpretation of TAM in small-sample contexts.

\section{Ethics and Data Handling}
The evaluation collected minimal personal data. Survey responses were anonymous,
and the system does not require real personal identity information for most
features. Where authentication is used, sessions are stored via random
identifiers and protected by HttpOnly cookies. GDPR considerations are discussed
in Chapter~5 \cite{ref_gdpr}.
