% !TEX root = ../Report.tex
% ======================================================================
\chapter{Conclusions and Future Work}
\label{ch:conclusions}
% ======================================================================

This chapter summarises achievements, critiques the system against its goals,
discusses limitations, and proposes future work.

\section{Conclusions}
GiTrip demonstrates that Git-like version control semantics can be meaningfully
applied to collaborative trip planning. The completed system meets the Must-have
objectives from the Project Specification:
\begin{itemize}
  \item repository-based trip storage with commits and branches,
  \item constraint-aware automatic scheduling integrating routing data,
  \item interactive timeline and map editing with commit saving,
  \item three-way merge with a dedicated conflict-resolution UI.
\end{itemize}

Evaluation results indicate that users can successfully
generate feasible itineraries and resolve merge conflicts within target times.
Survey feedback confirms perceived novelty and practical value, particularly for
group trips and scenarios requiring careful coordination.

\section{Critical Reflection and Lessons Learned}
Several lessons emerged during development and evaluation:
\begin{itemize}
  \item \textbf{Git concepts are powerful but cognitively expensive.} During
        Evaluation Day, even participants who understood the UI hesitated when
        encountering terms like branch and merge. The Easy mode toggle proved
        essential, but discoverability and mental model support remain ongoing
        work.
  \item \textbf{Structured merge is domain-specific.} Early iterations used
        \texttt{JSON.stringify}-based comparison, which caused subtle bugs when
        key ordering differed between branches. Switching to deep structural
        equality, stable IDs, and explicit deletion semantics resolved these
        issues but required substantial reworking of the merge engine.
  \item \textbf{Constraint scheduling requires explainability.} Feedback from
        testing showed that users trusted the auto-scheduler more when
        adjustments (e.g., opening-hours nudges) were visibly annotated with
        reasons.
  \item \textbf{External dependency management matters.} During development,
        OpenRouteService rate limits and occasional Google Directions failures
        highlighted the need for Haversine-based fallback strategies to keep the
        planner usable under degraded conditions.
\end{itemize}

\section{Limitations}
Key limitations include:
\begin{itemize}
  \item \textbf{Accessibility of interactive components:} maps and drag-based
        timelines remain challenging for keyboard-only and screen-reader users.
  \item \textbf{Merge granularity trade-offs:} while field-level conflicts are
        supported for selected fields, a fully general per-field resolver could
        overwhelm users.
  \item \textbf{No real-time collaboration:} GiTrip supports asynchronous
        collaboration via branches and merges, but not simultaneous live editing
        (CRDT/OT).
  \item \textbf{Heuristic scheduling:} the planner prioritises feasibility and
        responsiveness over global optimality.
\end{itemize}

Future work opportunities are substantial, spanning usability, collaboration
infrastructure, and algorithmic extensions.

\paragraph{Improved onboarding and guidance.}
Evaluation Day feedback consistently identified Git terminology as a source of
confusion, even among technically literate participants. Future iterations should
introduce in-product tutorials for branching and merging, contextual tooltips
that explain versioning actions in plain language, and clearer ``Save'' semantics
that reduce the gap between the user's mental model and the underlying commit
mechanism.

\paragraph{Accessibility enhancements.}
The current timeline and map editors rely on mouse-based drag interactions, which
remain inaccessible to keyboard-only and screen-reader users. Future work should
provide keyboard-operable alternatives for timeline edits (e.g.\ arrow keys with
step increments), text-based route editing as a fallback, and stronger Accessible Rich Internet Applications (ARIA)
landmark and live-region support throughout the application.

\paragraph{Real-time collaboration.}
GiTrip currently supports asynchronous collaboration via branches and merges.
A natural extension is to explore CRDT-based shared plan editing, enabling multiple users to edit the same itinerary
simultaneously while preserving a mergeable history model for offline and
divergent edits.

\paragraph{Richer merge resolution.}
The merge engine currently detects conflicts on a fixed set of fields (times,
name, coordinates, notes). Future versions could expand conflict detection to
additional metadata, include a live merged-plan preview within the resolution
UI, and support partial merges where users accept some changes and defer others.

\paragraph{Routing extensions.}
The current routing integration supports driving, walking, cycling, and transit
via ORS and Google Directions. Useful extensions include explicit support for
ferries and flights as route legs, integration with General Transit Feed
Specification (GTFS) data where
applicable, and improved offline routing approximations for areas with limited
API coverage.

\paragraph{Optional ML/AI extensions.}
Machine learning (ML) and AI-powered features were deliberately excluded from the MVP to preserve
determinism, explainability, and evaluation clarity (see
Section~\ref{sec:ai_scope}). However, they represent a clearly interesting
direction for future implementation. Potential applications include learning
user preferences (pace, activity types) to suggest better scheduling defaults,
predicting realistic dwell times and travel-time uncertainty from historical
data, and recommending destinations based on context. Any such extensions should
be implemented cautiously to maintain the explainability and deterministic
feasibility guarantees that the current system provides.

% ======================================================================
\chapter*{Author's Assessment of the Project}
\addcontentsline{toc}{chapter}{Author's Assessment of the Project}
% ======================================================================

\textbf{What is the (technical) contribution of this project?} GiTrip contributes
a practical system that applies Git-style branching, committing, and three-way
merging to structured itinerary data, integrated with constraint-aware scheduling
and interactive timeline/map editing.

\textbf{Why is this contribution relevant to Computer Science?} The project
connects software configuration management concepts (history, merging, conflict
resolution) with human-centred planning, demonstrating how domain semantics
change the design of storage, algorithms, and user interfaces.

\textbf{How can others make use of the work?} Developers can reuse the
snapshot-based repository model, merge engine patterns for structured JSON, and
the planner's constraint-handling approach in other collaborative planning
domains.

\textbf{Why should this project be considered an achievement?} It delivers an
end-to-end deployed application combining routing integration, a scheduler, and a
merge UI; evaluation shows users can complete core tasks successfully with limited
guidance.

\textbf{What are the limitations?} The main limitations are accessibility for
interactive controls, dependence on external routing providers, and the absence
of real-time collaboration and AI-based recommendation within the MVP scope.
